\vspace{-2cm}Formation Control of AAUSHIP

### 2015-10-29 paper.tex
Added additional citations
And included some text about it as well

>>>>

Previously research on using an autonomous surface vehicles (ASV) for bathymetry measurement has been reported in \cite{7271495, 5278235, 809261}, however, these were all operating independantly. Some preliminary studies in formation control of surface and sub-surface vehicles have been reported in \cite{7271700} where mechanically linked cooperative sub-surface vessels are considered, in \cite{4302258} where a non-linear approach to formation keeping of a group of surface vehicles is considered and in \cite{123}, where an inter-vessel force is introduced to keep the formation in place, which has certain parallels to the potential field approach, which is discussed in section \ref{sc:one-approach}. However, this is the first time that the formation control problem for ASVs is applied to bathymetry surveying.
